\chapter{Requirements and Constraints}
\label{Requirements_and_constraints}

Adding a WT to an existing water distribution network introduces new requirements and constraints on the system. 
\todo{wrong notation}
As mentioned in \secref{introduction}, a minimum pressure must be maintained in the PMAs for the end-users. Furthermore, the pressure can not exceed a maximum level as this might increase the possibility of water leakage and increase the wear on the pipes. The system described in \secref{system_overview}, is designed to operate at a pressure around 0.1 bar, relative to the environment \cite{master_aau}. For the purpose of this project the interval for which the pressure should be within, is chosen to be between $0.08 < \pmb{p_{cp}} < 0.14$ [Bar], where $p_{cp}$ is the pressure at a critical point.

Another important aspect when implementing a WT is water quality. If the water is stored, in the WT for too long the quality will decrease due to decreasing oxygen level, thus a requirement for water quality has to be formulated. As described in \secref{system_overview}, the WT has one combined input/output connection. Therefore a requirement only for flow is hard to formulate as the direction will change dependent on the usage. This could result in a flow based constraint being fulfilled by rapidly changing flow direction without actually replacing any significant water volume in the tower. Instead, a requirement for how often the content of the WT should be exchanged per time unit is proposed. For the purpose of this project the minimum requirement to volume exchange, is chosen to 30\% of the volume of $V_t$ per day. This can be written as $\bar{q}_{wt} > 0.3\cdot V_T \: \big[\frac{m^3}{day}\big]$. As stated in \secref{system_overview} $V_t = 200 \:L$ so therefore $\bar{q}_{wt} > 0.06 \: \big[\frac{m^3}{day}\big]$.

These constraints will due to the scope of the project be reduced and thus only contain a requirement for the pressure at each CP and a requirement to minimize the power consumption of the system. Thus will the requirement regarding water exchange in the WT not be investigated any further in this project. 
This results in the following remaining requirements:

\begin{itemize}
	\item Pressure at CP, $0.08 < \pmb{p_{cp}} < 0.14 \:[\text{bar}]$
%
	\item Minimizing the total cost of running the system
\end{itemize}
 