\section{Graph Representation}  
\label{GraphTheory}
A graph is a formal mathematical way for representing a network which can be applicable, among others, in engineering or scientific research, in mechanical systems or in electrical circuits and hydraulic networks \cite{graph_intro}. 

The modelling of the water distribution network is made with the help of Graph Theory. Each terminal of the network is associated with a node, and the components of the system correspond to edges \cite{GraphTheoryCarsten}. 
\subsection{Incidence Matrix} 
\label{IncidenceSection}
The incidence matrix, $\pmb{H}$, of a graph with \textit{n} nodes and \textit{e} edges is 
defined by $\pmb{H} = [a_{ij}]$. Where the number of rows and columns are defined by the amount of nodes and edges respectively. 
Additionally, the particular node and edge is denoted with the indices $i$ and 
$j$, respectively.

In case of a hydraulic network, the edges are directed in order to keep track of the direction of the flows in the system. It results in a directed incidence matrix as described below:

\begin{equation}
\label{DiGraph}
 a_{ij} =
		\left\{
		\begin{array}{ll}
		
		1 			&      \text{if the $j^{th}$ edge is incident out of the $i^{th}$ node}	
\\
		-1                       &     \text{if the $j^{th}$ edge is incident into the $i^{th}$ node}
\\


                0                       &      \text{otherwise}

		\end{array}
		\right.
\end{equation}	

In \appref{IncidenceSection} the corresponding incidence matrix of the system is 
shown. 

\subsection{Cycle Matrix}
\label{CycleSection}
A spanning tree, $T \in \mathcal{G}$ is a subgraph which contains all nodes of $\mathcal{G}$ but has no cycles \cite{GraphModel}. 
In order to obtain the spanning tree it is necessary to remove an edge from each cycle of the graph. The removed edges are called chords. To obtain the number of chords, $l$, the following applies:

\begin{equation}
  \label{Numberofchords}
  l = e - n +1
\end{equation}

Adding any additional chord to $T$, creates one cycle which is called fundamental cycle. A graph is conformed by as many fundamental cycles as number of chords it has \cite{GraphModel}.  
The set of fundamental cycles correspond to the fundamental cycle matrix $B$, such as the number of rows and columns are defined by the amount of chords and edges, respectively. 

The cycle matrix of a directed graph can be expressed with $\pmb{B} = [b_{ij}]$ where $i$ and $j$ denote the specific chords and 
edges respectively. 

\begin{equation}
\label{DiGraphCycle}
 b_{ij} =
		\left\{
		\begin{array}{ll}
		
		1 			&      \text{if the edges $j^{th}$ is in the cycle $i^{th}$ and the directions match}	
\\
		-1                       &     \text{if the edges $j^{th}$ is in the cycle $i^{th}$ and the directions are opposite}
\\

                0                       &      \text{otherwise}

		\end{array}
		\right.
\end{equation}	

In \appref{CycleAppendix} the corresponding incidence matrix of the system is 
shown.

\subsection{Kirchhoff's Law}
\label{KirchhoffSection}

The directed graph of a hydraulic network assigns two variables to each edges: 
the pressure, $\Delta p_k(t)$, and the flow, $q_k(t)$. These two variables are vectors containing the individual flows through the edges and 
the pressure across them:

% \begin{minipage}{0.45\linewidth}
% \begin{equation}
% p(t) =
% \begin{bmatrix}
%          p_1 \\
% 	p_2 \\ 
% 	\vdots \\
% 	p_e \\
% \end{bmatrix}  \nonumber
% \end{equation}  
% \end{minipage}

% \begin{minipage}{0.45\linewidth}
%  \begin{equation}
% q(t) =
% \begin{bmatrix}
%          q_1 \\
% 	q_2 \\ 
% 	\vdots \\
% 	q_e \\
% \end{bmatrix}
% \end{equation}
% \end{minipage}

\begin{equation}
%\[
\pmb{\Delta p(t)} =
\begin{bmatrix}
         \Delta p_c \\
	\Delta p_f \\ 
	\vdots \\
	\Delta p_e \\
\end{bmatrix}
\text{and}\hspace{0.3cm}
\pmb{q(t)} =
\begin{bmatrix}
         q_c \\
	q_f \\ 
	\vdots \\
	q_e \\
\end{bmatrix}
%\]
\end{equation}


In order to derive a model of the hydraulic network a set of independent flow variables has to be identified \cite{TowerModel}. These flow variables have the characteristic 
that their values can be set independently from other flows in the network, and coincide with the flows through the chords. 
Therefore, it has been decided to choose the numbering of the columns of the 
$\pmb{H}$ and $\pmb{B}$ matrix, such as:

% \begin{minipage}{0.45\textwidth}
% \begin{equation}
% H = [H_c \quad H_f]
% \end{equation}   \nonumber
% \end{minipage}

% \begin{minipage}{0.45\textwidth}
% \begin{equation}
% B = [B_c  \quad B_f]
% \end{equation}
% \end{minipage}

\begin{equation}
%\[
\pmb{H} = [\pmb{H_c} \quad \pmb{H_f}]
\hspace{0.1cm} \text{and}\hspace{0.3cm}
\pmb{B} = [\pmb{B_c}  \quad \pmb{B_f}] = [\pmb{I} \quad \pmb{B_f}]
%\]
\label{HandB}
\end{equation}

\begin{minipage}[t]{0.20\textwidth}
Where\\
\hspace*{8mm} $\pmb{H_c} \quad \text{and} \quad \pmb{B_c}$ \\
\hspace*{8mm} $\pmb{H_f} \quad \text{and} \quad \pmb{B_f}$ 
\end{minipage}
\begin{minipage}[t]{0.68\textwidth}
\vspace*{2mm}
\hspace*{8mm} are the matrices corresponding to the chords,\\
\hspace*{8mm} are the matrices corresponding to the spanning tree. 
\end{minipage}

Since the edges variables are elements interconnected to form a network, 
they must obey the law of conservation of mass and pressure \cite{GraphModel}. 

Kirchhoff´s Current Law (KCL) states that the net sum of all the flows leaving and entering the node is zero. Formulating this statement in matrix form:

\begin{equation}
  \label{KCL}
  \pmb{H} \cdot \pmb{q(t)} = 0
\end{equation}

Furthermore, regarding Kirchhoff´s Voltage Law (KVL) it is stated that at any time the net sum of the pressure around a cycle 
is zero. In terms of matrix form:

\begin{equation}
 \label{KVL} 
 \pmb{B} \cdot \pmb{\Delta p (t)} = 0
\end{equation}

Where the fundamental loops have a reference direction given by the direction of the 
chords. 





 