\section{Model Parameters}
\label{estimateParameters}
In order to obtain a complete model of the physical setup, all the parameters describing the components have to be defined. Usually, these parameters can be 
obtained from the data sheets provided by the manufactures. Nevertheless, some components can change their characteristics over time, which introduces uncertainties 
into the model. Hence, in the current chapter a detailed compilation of the known/unknown parameters of the physical water distribution setup is carried out.

\subsection{Known Parameters}

The model parameters that are taken to be known are introduced below and can be found in \appref{system_description}.


\begin{itemize}
  \item The parameters corresponding to the pumps such that: $a_{h0}$, $a_{h1}$, $a_{h2}$. %The values of this parameters are provided by the manufacturer of the pumps, Grundfos, and can be found in the.
  
  \item In regards to the valves, the variable taking part on the modelling of a valve is the conductivity function $\pmb{k_v(OD)}$. However, in 
  order to describe the valve characteristic function, other parameters have to be introduced i.e. the curve factor $n_{gl}$, and the 
  valve maximum, $\theta_{max}$, and minimum, $\theta_{off}$ opening degree.
  
  \item In the modelling of the pipes three parameters are considered as known. The length of the pipes $L$, their diameter $D$, and the change of 
  elevation across each pipe $\Delta Z$.  
\end{itemize} 

\subsection{Unknown Parameters}
The unknown parameters are the ones related with the form losses, $k_f$, and form friction ,$f$, of the pipes. Despite they are 
provided by the manufactures they need to be estimated. On the one hand, the form losses depend on the fittings and bends of the pipes which they are not always known. 
On the other hand, the friction losses dependent on the inside average roughness of pipes, $\epsilon$, which can change its value due to passage of time 
and the rust generated inside pipes. 

%The friction and form losses are part of the model of a pipe, and are given by the following equation
%
%\begin{equation}
%  \lambda (q) =  \frac{8fL}{\pi^{2}gD^5} \rho g  |q| q + k_f \frac{8}{\pi^2gD^4} \rho g |q| q
%  \label{frictionestimation}
%\end{equation}

%From the above equation it can be seen that either estimating only for $k_f$ or $f$ will have the same result in the value of $\lambda (q)$.
%Therefore, it has been decided to carry out the estimation of the total value of $\lambda (q)$, hence discarding the respective values of $k_f$ and $f$.

Furthermore, the operating points of the flow through the chords, $\pmb{\bar{z}}$, is also unknown. These values, which correspond to the $8$ flow chords, are introduced in the linearized expression of both pipes 
and valves, see \eqref{lambda_lin} and \eqref{mu_lin}. Thus, not only pipe parameters introduce uncertainties into the system model but also the lack of knowledge of the chord operating points.

Consequently, it has been decided to estimate the total expression for the pressure across the pipes and valves in order to reduce the amount of unknowns in the system.

The system has $15$ pipes in total,  from \eqref{lambda_lin} it can be seen that either tunning for $k_f$, $f$ or $\pmb{\bar{z}}$ it will have the same result for the total
value of the pressure across the pipes, $\lambda(\pmb{{B_1^{T}}}\pmb{z})$. For this reason the pressure across the 15 pipes is estimated.

Valve linearized expression, see \eqref{mu_lin}, consists on the term depending on the chord flows and the one depending on the $OD$. Both terms include the operating 
point of the chord flows inside them, thus, the pressure difference given by both terms has to be estimated. In the system 4 valves take part, 
resulting in 8 unknowns in total. 

The WT connection edge, see \eqref{gamma_lin}, is conformed by two valves and one pump. Although the parameters corresponding to the pump are considered as known, the ones 
corresponding to the valves have to be estimated. Resulting in two more unknowns for the system. 

All in all, the system has $24$ unknown terms which will be calculated following the estimation process described in the next section.